{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-07-29 swmp_noise.tex
added data for case studies with multiple window combs, fixed tables, started some agg plots for metab

% example from SAPDC
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=0.8\textwidth]{figure/case_ex1}

\caption[Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression]{Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Sapelo Island station.\label{fig:case_ex1}}
\end{figure}

% example from ELKVM
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=0.8\textwidth]{figure/case_ex2}

\caption[Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression]{Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Elkhorn Slough station.\label{fig:case_ex2}}
\end{figure}

% example from pdbby
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=0.8\textwidth]{figure/case_ex3}

\caption[Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression]{Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Padilla Bay station.\label{fig:case_ex3}}
\end{figure}

@@

% correlations with tide before/after wtreg
% latex.default(tab, file = "", rowlabel = "Site", rgroup = unique(rows),      n.rgroup = rep(2, 4), insert.bottom = foot.val, caption = cap.val,      colheads = c("DO", "DO flux", "Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), caption.loc = "top", rowname = rep(c("Observed",          "Detided"), 4), label = "tab:cor_res") 
%
\begin{table}[!tbp]
\caption{Correlations of tidal changes at each site with continuous \ac{DO} observations, instantaneous \ac{DO} flux, and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after detiding with weighted regression.  \ac{DO} values are correlated with predicated tidal height at each observation, \ac{DO} flux values are correlated with tidal change between observations, and daily integrated metabolism estimates are correlated with daily tidal range.\label{tab:cor_res}} 
\begin{center}
\begin{tabular}{llllll}
\hline\hline
\multicolumn{1}{l}{Site}&\multicolumn{1}{c}{DO}&\multicolumn{1}{c}{DO flux}&\multicolumn{1}{c}{Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{Rt}&\multicolumn{1}{c}{NEM}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&\tabularnewline
~~Observed& 0.48***& 0.26***& 0.05 & 0.00 & 0.08 \tabularnewline
~~Detided& 0.01 &-0.04***&-0.01 & 0.06 & 0.07 \tabularnewline
\hline
{\bfseries PDBBY}&&&&&\tabularnewline
~~Observed&-0.45***&-0.31***&-0.12*& 0.03 &-0.10 \tabularnewline
~~Detided& 0.00 & 0.02**& 0.08 &-0.17**&-0.12*\tabularnewline
\hline
{\bfseries RKBMB}&&&&&\tabularnewline
~~Observed& 0.28***& 0.39***& 0.03 & 0.09 & 0.21***\tabularnewline
~~Detided&-0.01 & 0.02*&-0.08 & 0.16**& 0.18**\tabularnewline
\hline
{\bfseries SAPDC}&&&&&\tabularnewline
~~Observed& 0.48***& 0.62***&-0.02 & 0.00 &-0.04 \tabularnewline
~~Detided&-0.01 &-0.04***&-0.04 &-0.03 &-0.10*\tabularnewline
\hline
\end{tabular}
\end{center}
\footnotesize *$p<0.05$; **$p<0.01$; ***$p<0.001$\\\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}

% case study metabolism results, including perc anom
% latex.default(tab, file = "", rowlabel = "Site", insert.bottom = foot.val,      caption = cap.val, caption.loc = "top", rgroup = gsub("_wtreg.RData",          "", unique(to_tab$Site)), n.rgroup = rep(2, 4), cgroup = c("Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), n.cgroup = c(3, 3, 2), rowname = rows,      colheads = c(rep(c("Mean", "Std. Err.", "Anom"), 2), c("Mean",          "Std. Err.")), label = "tab:case_res") 
%
\begin{table}[!tbp]
\caption{Metabolism estimates (gross production, respiration, and net metabolism) for case studies using \ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.\label{tab:case_res}} 
\begin{center}
\begin{tabular}{llllclllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Site}&\multicolumn{3}{c}{\bfseries Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Rt}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NEM}\tabularnewline
\cline{2-4} \cline{6-8} \cline{10-11}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&&&&&&\tabularnewline
~~Observed&5.42&0.70&0.28&&-8.58&0.78&0.23&&-3.16&0.40\tabularnewline
~~Detided&0.02&0.54&0.39&&-2.47&0.51&0.33&&-2.45&0.37\tabularnewline
\hline
{\bfseries PDBBY}&&&&&&&&&&\tabularnewline
~~Observed&8.03&0.70&0.20&&-8.59&0.78&0.16&&-0.56&0.57\tabularnewline
~~Detided&6.31&0.65&0.22&&-6.97&0.67&0.24&&-0.66&0.49\tabularnewline
\hline
{\bfseries RKBMB}&&&&&&&&&&\tabularnewline
~~Observed&2.46&0.14&0.14&&-3.24&0.16&0.10&&-0.78&0.09\tabularnewline
~~Detided&2.59&0.12&0.11&&-3.28&0.15&0.09&&-0.69&0.08\tabularnewline
\hline
{\bfseries SAPDC}&&&&&&&&&&\tabularnewline
~~Observed&4.46&0.25&0.17&&-6.37&0.27&0.11&&-1.90&0.15\tabularnewline
~~Detided&4.48&0.17&0.09&&-6.12&0.20&0.05&&-1.65&0.12\tabularnewline
\hline
\end{tabular}
\end{center}
\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}

>>>>

@@

% correlations with tide before/after wtreg
% latex.default(tab, file = "", rowlabel = "Site", rgroup = unique(rows),      n.rgroup = rep(2, 4), insert.bottom = foot.val, caption = cap.val,      colheads = c("DO", "DO flux", "Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), caption.loc = "top", rowname = rep(c("Observed",          "Detided"), 4), label = "tab:cor_res") 
%
\begin{table}[!tbp]
\caption{Correlations of tidal changes at each site with continuous \ac{DO} observations, instantaneous \ac{DO} flux, and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after detiding with weighted regression.  \ac{DO} values are correlated with predicted tidal height at each observation, \ac{DO} flux values are correlated with tidal change between observations, and metabolism estimates are correlated with mean tidal change between observations during day, night, or total, day periods for production, respiration, and net metabolism respectively.  Total day periods were defined as the approximate 24 hours between sunrises for two calendar days, where day was the time from sunrise to sunset and night was the following time from sunset to sunrise.  Results are for weighted regressions using a window of thirty days and tidal height proportion of one.\label{tab:cor_res}} 
\begin{center}
\begin{tabular}{llllll}
\hline\hline
\multicolumn{1}{l}{Site}&\multicolumn{1}{c}{DO}&\multicolumn{1}{c}{DO flux}&\multicolumn{1}{c}{Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{Rt}&\multicolumn{1}{c}{NEM}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&\tabularnewline
~~Observed& 0.47***& 0.26***& 0.60***& 0.73***& 0.35***\tabularnewline
~~Detided& 0.01 &-0.04***&-0.08 &-0.17**&-0.01 \tabularnewline
\hline
{\bfseries PDBBY}&&&&&\tabularnewline
~~Observed&-0.45***&-0.31***&-0.33***&-0.46***&-0.24***\tabularnewline
~~Detided&-0.02*& 0.01 & 0.23***& 0.12*&-0.10 \tabularnewline
\hline
{\bfseries RKBMB}&&&&&\tabularnewline
~~Observed& 0.28***& 0.39***& 0.35***& 0.40***& 0.26***\tabularnewline
~~Detided&-0.01 & 0.02**&-0.23***&-0.20***& 0.01 \tabularnewline
\hline
{\bfseries SAPDC}&&&&&\tabularnewline
~~Observed& 0.48***& 0.62***& 0.53***& 0.70***& 0.40***\tabularnewline
~~Detided&-0.01 &-0.03***& 0.04 & 0.15**&-0.02 \tabularnewline
\hline
\end{tabular}
\end{center}
\footnotesize *$p<0.05$; **$p<0.01$; ***$p<0.001$\\\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}

% case study metabolism results, including perc anom
% latex.default(tab, file = "", rowlabel = "Site", insert.bottom = foot.val,      caption = cap.val, caption.loc = "top", rgroup = unique(to_tab$Site),      n.rgroup = rep(2, 4), cgroup = c("Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), n.cgroup = c(3, 3, 2), rowname = rows,      colheads = c(rep(c("Mean", "Std. Err.", "Anom"), 2), c("Mean",          "Std. Err.")), label = "tab:case_res") 
%
\begin{table}[!tbp]
\caption{Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regressions with a window of thirty days and tidal height proportion of one.\label{tab:case_res}} 
\begin{center}
\begin{tabular}{llllclllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Site}&\multicolumn{3}{c}{\bfseries Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Rt}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NEM}\tabularnewline
\cline{2-4} \cline{6-8} \cline{10-11}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&&&&&&\tabularnewline
~~Observed&8.14&0.67&0.19&&-8.19&0.69&0.21&&-0.05&0.16\tabularnewline
~~Detided&2.65&0.41&0.27&&-2.68&0.43&0.29&&-0.03&0.14\tabularnewline
\hline
{\bfseries PDBBY}&&&&&&&&&&\tabularnewline
~~Observed&5.95&0.69&0.22&&-5.90&0.74&0.19&& 0.05&0.22\tabularnewline
~~Detided&5.07&0.53&0.24&&-5.00&0.57&0.28&& 0.07&0.21\tabularnewline
\hline
{\bfseries RKBMB}&&&&&&&&&&\tabularnewline
~~Observed&3.02&0.14&0.09&&-3.62&0.15&0.08&&-0.60&0.06\tabularnewline
~~Detided&3.03&0.13&0.09&&-3.62&0.14&0.07&&-0.59&0.06\tabularnewline
\hline
{\bfseries SAPDC}&&&&&&&&&&\tabularnewline
~~Observed&4.89&0.23&0.13&&-6.04&0.25&0.11&&-1.16&0.09\tabularnewline
~~Detided&4.61&0.16&0.07&&-5.80&0.17&0.04&&-1.19&0.08\tabularnewline
\hline
\end{tabular}
\end{center}
\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}
